The Eclipse Integrated Computational Environment

### 2019-08-06 src/content.tex
Addressed comments from Mike Guidry.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

It is not clear which, if any, of these solutions is better than the
others, and practical requirements will ultimately dictate the path of a
project's progress. This work considers a middle ground solution and
presents the Eclipse Integrated Computational Environment (ICE) as proof
that it is possible to create such a system. Specifically, the work
described here shows that

@@

The most obvious workflow for any individual simulation code or
collection of codes is to string the activities together, where the user's
workflow is to create the input, launch the job, perform some analysis,
and manage the data---possibly modifying the code in the process. However, 
there are many other combinations, including re-running jobs with
conditions or modifications or analyzing someone else's data.\footnote{The
authors have identified many unique combinations that
define workflow ``classes.'' When possible, every effort is made to give the
classes colloquial names such as ``The Re-Run'' or ``The Graduate Student.''}

@@

Eclipse ICE is an open-source project, and the authors welcome and encourage
engagement and contributions from users. Interested parties may inquire by
contacting the corresponding author or visiting the ICE website.

>>>>

It is not clear which, if any, of these solutions is better than the
others, and practical requirements will ultimately dictate the path of a
project's progress. This chapter considers a middle ground solution and
presents the Eclipse Integrated Computational Environment (ICE) as proof
that it is possible to create such a system. Specifically, the work
described here shows that

@@

The most obvious workflow for any individual simulation code or
collection of codes is to string the activities together, where the user's
workflow is to create the input, launch the job, perform some analysis,
and manage the data---possibly modifying the code in the process. However, 
there are many other combinations, including re-running jobs with
conditions or modifications or analyzing someone else's data.\footnote{The
author has identified many unique combinations that
define workflow ``classes.'' When possible, every effort is made to give the
classes colloquial names such as ``The Re-Run'' or ``The Graduate Student.''}

@@
